Time-series modeling of epidemics in complex populations: detecting changes in incidence volatility over time

### 2024-12-20 ms-3/ms.tex

\section*{Results and Discussion}
Our estimates of $\theta$ were robust across the population sizes included in the empirical analysis of U.S. counties. 
However, inaccuracies were more common in counties with small populations outside the examined range.%(\nameref{S1_Fig}). 
We found that the LRT method of testing for sharp changes in $\theta$ is also robust across population sizes represented in the empirical data (Fig\ 1 e, f). 
Adequate test performance is characterized by an average \( p \)-value of 0.5 when the effect size is zero, with decreasing average $p$-values as the effect size increases.

\begin{figure}[!ht]
\includegraphics[width=1\textwidth]{fig1}
\caption{
Detecting changes in dispersion within incidence time series for populations of different sizes. (a, b) Simulated case counts with constant (a) and changing (b) dispersion parameters. (c, d) Dispersion parameters used to generate the data in (a) and (b), respectively. (e, f) LRT performance under varying absolute differences in \(\theta\) (horizontal axis), showing \( p \)-value distributions for population sizes of 50,000 (e) and 10,000,000 (f), representing the range in the empirical data. The null and alternative hypotheses (O and X) correspond to the parameters in (c) and (d). Red vertical lines indicate interquartile ranges.
}\label{fig1}
\end{figure}

>>>>

\section*{Results and Discussion}
Our estimates of $\theta$ were robust across the population sizes included in the empirical analysis of U.S. counties. 
However, inaccuracies were more common in counties with small populations outside the examined range.%(\nameref{S1_Fig}). 
We found that the LRT method of testing for sharp changes in $\theta$ is also robust across population sizes represented in the empirical data (Fig\ 1 e, f). 
Adequate test performance for the LRT is characterized by an average \( p \)-value of 0.5 when the effect size is zero, with decreasing average $p$-values as the effect size increases.

%\begin{figure}[!ht]
%\includegraphics[width=1\textwidth]{fig1}
%\caption{
%Detecting changes in dispersion within incidence time series for populations of different sizes. (a, b) Simulated case counts with constant (a) and changing (b) dispersion parameters. (c, d) Dispersion parameters used to generate the data in (a) and (b), respectively. (e, f) LRT performance under varying absolute differences in \(\theta\) (horizontal axis), showing \( p \)-value distributions for population sizes of 50,000 (e) and 10,000,000 (f), representing the range in the empirical data. The null and alternative hypotheses (O and X) correspond to the parameters in (c) and (d). Red vertical lines indicate interquartile ranges.
%}\label{fig1}
%\end{figure}
